\Title

### 2021-07-14 manuscript/content.tex
Add something about the CV results

We determined the depth of the sources and the damping parameter by applying
K-Fold cross-validation through the scikit-learn library \citep{sklearn2011}.
The method randomly divides the original data into $k$ sets (folds), fits the
model using only data from $k - 1$ folds, and validates the model by comparing
its predictions against the one remaining fold.
This process is carried out once for each one of the $k$ folds, leading to
an estimated mean cross-validation RMS error for the model.
To speed up the computation, we only performed the cross-validation on a subset
of the data corresponding to an area of
\AustraliaSmallAreaEastingSize{}$\times$\AustraliaSmallAreaNorthingSize{}
containing \AustraliaSmallAreaNPoints{} points.
We ran the cross-validation repeatedly for combinations of \emph{depth},
ranging from \AustraliaDepthMin{} to \AustraliaDepthMax{},
and \emph{damping}, from \AustraliaDampingMin{} to \AustraliaDampingMax{} in
steps of one order of magnitude.
Figure \ref{fig:australia-memory-cv-error}b shows the resulting
cross-validation RMS errors and highlights the minimum value of
\AustraliaEqlRmsScore{}, which corresponds to a relative depth of
\AustraliaEqlDepth{} and a damping equal to \AustraliaEqlDamping{}.

@@

Fig.~\ref{fig:australia} shows the original data distribution and the
interpolated grid.
Grid points that are further than 50\km{} from the nearest data point are
masked to avoid unrealistic extrapolations.
Fig.~\ref{fig:australia-memory-cv-error}c shows the RMS error against the
observed data after each iteration of the algorithm.
Fig.~\ref{fig:australia-residuals} shows the difference between the observed
and predicted gravity disturbances.
The inset figure shows a histogram of these residuals, which are approximately
normally distributed around zero.

@@

>>>>

We determined the depth of the sources and the damping parameter by applying
K-Fold cross-validation through the scikit-learn library \citep{sklearn2011}.
The method randomly divides the original data into $k$ sets (folds), fits the
model using only data from $k - 1$ folds, and validates the model by comparing
its predictions against the one remaining fold.
This process is carried out once for each one of the $k$ folds, leading to
an estimated mean cross-validation RMS error for the model.
To speed up the computation, we only performed the cross-validation on a subset
of the data corresponding to an area of
\AustraliaSmallAreaEastingSize{}$\times$\AustraliaSmallAreaNorthingSize{}
containing \AustraliaSmallAreaNPoints{} points.
We ran the cross-validation repeatedly for combinations of \emph{depth},
ranging from \AustraliaDepthMin{} to \AustraliaDepthMax{},
and \emph{damping}, from \AustraliaDampingMin{} to \AustraliaDampingMax{} in
steps of one order of magnitude.
Figure \ref{fig:australia-memory-cv-error}c shows the resulting
cross-validation RMS errors and highlights the minimum value of
\AustraliaEqlRmsScore{}, which corresponds to a relative depth of
\AustraliaEqlDepth{} and a damping equal to \AustraliaEqlDamping{}.

@@

Fig.~\ref{fig:australia} shows the original data distribution and the
interpolated grid.
Grid points that are further than 50\km{} from the nearest data point are
masked to avoid unrealistic extrapolations.
Fig.~\ref{fig:australia-memory-cv-error}b shows the RMS error against the
observed data after each iteration of the algorithm.
Fig.~\ref{fig:australia-residuals} shows the difference between the observed
and predicted gravity disturbances.
The inset figure shows a histogram of these residuals, which are approximately
normally distributed around zero.

@@

The elongated valley around the minimum of the cross-validation RMS errors
(Fig.~\ref{fig:australia-memory-cv-error}c) shows that there is ambiguity in
the choice of damping and source depths.
One could choose a large damping with a small depth or a small damping with a
large depth to achieve roughly the same interpolation result.
This is expected since both parameters control the smoothness of the
interpolation.
